Flattering Advice: Avoiding Disappointment as a Driver of Gender Discrimination

### 2024-01-14 manuscript/manuscript.Rmd
Study 1.

## Discussion
When the quality of a decision is not dependent on someone's expectations,
advice should not be moved by whether an adviser is aware of the advisees
expectations. However, consistent with our account that advisers consider the
belief utility of the advisee and want to flatter, rather than disappoint them,
we find that displaying expectations to advisers does matter.
Specifically, we found that men underestimate their score on a mathematics test
less than do women. When these expectations are displayed to advisers, they
are more likely to tell men to compete against the High Performer group.
Notably, this is bad advice: men's expected earnings decreases if their
expectations are shown to advisers.

<!-- David: One more sentence about the earnings difference here, which does not -->
<!-- differ significantly. And one sentence about the new analysis of whether -->
<!-- people follow the advice or not. -->

>>>>

## Discussion

In Study 1, we discovered that although advisers are encouraged to
provide accurate advice, they still take into account the expectations
of advisees, which are irrelevant to the utility of the advice. Due to
the fact that males tend to be more confident than their equally
competent female counterparts, they are more likely to be recommended to
compete against high-performance competitors. However, when advice is
given to match the advisees' expectations, these flattering
recommendations result in lower expected bonus earnings for male
participants.
